Implementation and Analysis of Homomorphic Facial Image Encryption and Manipulation

### 2019-03-17 icmssp-paper/parts/01_introduction.tex
Shortening Ch2-3

In the area of homomorphic image encryption, there is interest in being able to perform image manipulation operations such as image adjustment, image filtering, and morphological extraction operations~\cite{ziad_cryptoimg:_2016, gonzalez_digital_2008}. The \textit{CryptoImg} software library implements common linear operations on encrypted images~\cite{ziad_cryptoimg:_2016}. There is also work on facial recognition on encrypted images\cite{turk_eigenfaces_1991, hutchison_privacy-preserving_2009}. However, preprocessing which requires non-linear operations, such as those in~\cite{oravec_illumination_2010}, has yet to be performed in the encrypted domain.

@@

To investigate the applicability of homomorphic image manipulation, in Section \ref{sec:chapter_2}, we introduce three homomorphic cryptosystems prominent in the literature: Paillier, Damg{\aa}rd--Geisler--Kr{\o}igaard (DGK), and Brakerski--Gentry--Vaikuntanathan (BGV) cryptosystems. We list important properties of each cryptosystem and show how they can be used for non-linear image processing operations, compared to previous uses in the literature. In Section \ref{sec:chapter_3}, we implement a software library allowing for common linear and non-linear image processing operations using each of the three cryptosystems, assuming a client-server model for secure computation.

>>>>

In the area of homomorphic image encryption, there is interest in being able to perform image manipulation operations such as image adjustment, image filtering, and morphological extraction operations~\cite{ziad_cryptoimg:_2016, gonzalez_digital_2008}. There is also work on facial recognition on encrypted images\cite{turk_eigenfaces_1991, hutchison_privacy-preserving_2009}. While secure linear image operations have been implemented~\cite{ziad_cryptoimg:_2016}, preprocessing which requires non-linear operations, such as those in~\cite{oravec_illumination_2010}, has yet to be performed in the encrypted domain.

@@

To investigate the applicability of homomorphic image manipulation, in Section \ref{sec:chapter_2}, we introduce three homomorphic cryptosystems prominent in the literature: the Paillier, Damg{\aa}rd--Geisler--Kr{\o}igaard (DGK), and Brakerski--Gentry--Vaikuntanathan (BGV) cryptosystems, as well as relevant past implementations. In Section \ref{sec:chapter_3}, we implement a software library allowing for common linear and non-linear image processing operations using each of the three cryptosystems, assuming a client-server model for secure computation.
